\begin{thebibliography}{}
\bibitem{stat-regression}
Mendenhall, William & Sincich, Terry. (1997). A Second Course in Statistics: Regression Analysis. Journal of the American Statistical Association. 92. 10.2307/2965740. 

\bibitem{ozone-assesment}
WMO (World Meteorological Organization), Scientific Assessment of Ozone Depletion: 2018, Global Ozone Research and Monitoring Project – Report No. 58, 588 pp., Geneva, Switzerland, 2018.

\bibitem{process-based}
Wohltmann, I., Rex, M., Brunner, D., M ̈ader, J.. (2005). Integrated equivalent latitude as a proxy for dynamical changes in ozone column. Geophysical Research Letters. 3210. 1029/2005GL022497.​
\bibitem{EESC-ref}
Newman, P. A., Daniel, J. S., Waugh, D. W., and Nash, E. R.. A new formulation of equivalent effective stratospheric chlorine (EESC), Atmos. Chem. Phys., 7, 4537–4552, https://doi.org/10.5194/acp-7-4537-2007, 2007.

\bibitem{trend-NP}
Bojkov, R. D., L. Bishop, W. J. Hill, G. C. Reinsel, and G. C. Tiao (1990), A statistical trend analysis of revised Dobson total ozone data over the northern hemisphere, J. Geophys. Res., 95, 9785–9807.

\bibitem{dynamic-proxy}
Ziemke, J., S. Chandra, R. McPeters, and P. Newman (1997), Dynamical proxies of column ozone with applications to global trend models, J. Geophys. Res., 102(D5), 6117– 6129.

\bibitem{bolder}
CLUE: Chemistry, Life, the Universe, and Everything. (2022, April 3). Michigan State University and UC Bolder.https://chem.libretexts.org/@go/page/354112

\bibitem{brute-force}
Mäder, J. A., Staehelin, J., Brunner, D., Stahel, W. A., Wohltmann, I., and Peter, T. (2007), Statistical modeling of total ozone: Selection of appropriate explanatory variables, J. Geophys. Res., 112, D11108, doi:10.1029/2006JD007694.

\bibitem{data-set}
Halogen Chemistry dataset reference:\\
https://gml.noaa.gov/dv/data.html\\
https://agage.mit.edu/data/agage-data\\
https://gml.noaa.gov/hats/odgi.html\\

\bibitem{dataset-2}
QBO dataset reference:\\
https://www.geo.fuberlin.de/en/met/ag/strat/produkte/qbo/index.html

\bibitem{dataset-3}
Heterogeneous Polar Chemistry dataset reference\\
https://openbooks.lib.msu.edu/clue/chapter/chapter-4-heterogeneous-compounds/

\bibitem{data-set-4}
Aerosol dataset reference:\\
https://data.giss.nasa.gov/modelforce/strataer//tau.line$_$2012.12.txt

\bibitem{data-set-5}
Solar Cycle dataset reference:\\ 
https://www.ngdc.noaa.gov/stp/space-weather/solar-data/solar-features/solar-radio/
 
\end{thebibliography}